Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2021-05-09 Article.Rmd
Subpopulation and minor corrections

```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#Load required packages :
library(tidyverse)
library(readr)
library(scales)
library(ggplot2)
library(ggpubr)

#Load the data from the .csv files
source("./scripts/read_overview.R", local = knitr::knit_global())

#Source the scripts used to manipulate the data from the .csv files
source("./scripts/create_year_design.R", local = knitr::knit_global())
source("./scripts/create_design_data.R", local = knitr::knit_global())
source("./scripts/create_location_data.R", local = knitr::knit_global())
source("./scripts/create_sample.R", local = knitr::knit_global())

@@

The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in \@ref(fig:PlotYear). Apart from the quantitative increase in the number of studies, there's also a qualitative increase in the diversity of the studies, both in the type of design used and the countries where the studies are conducted.

@@

However, despite this growing diversity, the vast majority of studies are conducted in North America (N = `r North_America_studies`), with a large predominance of studies in the United States of America (N= `r max(year_country$cumulative_location[year_country$location == "USA"])`). The majority of the remaining studies were then located in Asia (N = `r Asia_studies`) or in Europe (N = `r Europe_studies`). South America and Africa were the least represented continents, with only `r South_America_studies` and `r Africa_studies` studies respectively.

In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r N_cross_sec`). The number of longitudinal studies steadily grew since 2014 but only represents `r percent(N_long/109)` of the papers to this day. Qualitative studies are also under-represented, with only `r N_qual` papers. Of note, we only identified 1 mixed design @buttram2015 ; this study employed a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part. The first systematic reviews and meta-analyses were published recently, in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])` while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.

@@

>>>>

```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#Load required packages :
library(tidyverse)
library(readr)
library(scales)
library(ggplot2)
library(ggpubr)
library(sunburstR)
library(d3r)

#Load the data from the .csv files
source("./scripts/read_data.R", local = knitr::knit_global())

#Source the scripts used to manipulate the data from the .csv files
source("./scripts/create_year_design.R", local = knitr::knit_global())
source("./scripts/create_location_data.R", local = knitr::knit_global())
source("./scripts/create_sample.R", local = knitr::knit_global())

@@

The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in Figure \@ref(fig:PlotYear). Apart from the quantitative increase in the number of studies, there's also a qualitative increase in the diversity of the studies, both in the type of design used and the countries where the studies are conducted.

@@

However, despite this growing diversity, the vast majority of studies are conducted in North America (N = `r .North_America_studies`), with a large predominance of studies in the United States of America (N= `r .USA_studies`). The majority of the remaining studies were then located in Asia (N = `r .Asia_studies`) or in Europe (N = `r .Europe_studies`). South America and Africa were the least represented continents, with only `r .South_America_studies` and `r .Africa_studies` studies respectively.

In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r .N_cross_sec`). The number of longitudinal studies steadily grew since 2014 but only represents `r percent(.N_long/109)` of the papers to this day. Qualitative studies are also under-represented, with only `r .N_qual` papers. Of note, we only identified 1 mixed design @buttram2015 ; this study employed a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part. The first systematic reviews and meta-analyses were published recently, in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])` while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.

@@

```{r Subpopulation_data_prep, message=FALSE, warning=FALSE, include=FALSE}
library(cowplot)
source("./scripts/create_population_data.R", local = knitr::knit_global())
source("./scripts/create_population_plot.R", local = knitr::knit_global())

A bit less than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focus on a subpopulation of MSM. In this review, we identified 6 kind of MSM subpopulations studied in syndemic literature : (a) young MSM and older MSM ; (b) MSM from a racial/ethnic minority ; (c) MSM living with HIV ; (d) MSM engaged in sex work ; (e) Men who have Sex with Men and Women (MSMW) ; and (f) transgender MSM.

Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r sum(population$age == "Older men")` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r sum(population$age == "Adolescent")` study focuses on adolescents[@Perry]. Of note, the two studies on older MSM are both entirely composed of a sample of older MSM living with HIV.

Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample. Among these studies, `r .N_YBMSM` studies are composed of young BMSM[@Maiorana; @Reed2016] and `r .N_MSM_SW` study focuses on Black MSM engaged in sex work[@chandler2020]. \
Only (N= `r sum(population$race_ethnicity == "Latino")`) studies focus on Latino MSM (LMSM) and `r .N_LMSMW` of these studies focus on Latino MSMW[@Munoz-Laboy2018]. Furthermore, `r sum(population$race_ethnicity == "Latino & Black")` study focus on both BMSM and LMSM[@cassels2020].

Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV. Apart from the aforementioned studies on older MSM living with HIV, `r sum(population$serologic_status == "HIV-positive" & population$age == "Young adult")` studies focus on young MSM living with HIV[@Lyons2013; @Bruce2011] . Notably, we identified no studies conducted on racial minority MSM living with HIV.

Finally, the least represented subpopulation of MSM in this review are MSMW (N = `r sum(population$sex_behav == "MSMW")`), MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`). Strikingly, transgender MSM, in addition to being the focus of only one study[@Reisner2016a] are, by design, excluded from every other study whereas other MSM subpopulation are at least partially represented in most of the samples.

Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.

In order to have the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also measured took into account studies who did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulation. \
`r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].

```{r PlotPop, fig.cap = "Number of studies focusing on a MSM subpopulation, by kind of subpopulation"}

knitr::include_graphics("./Output/Plots/Plot_population.png")
```
